The Fremont Frontier \\\large{Living at the Margins of Maize Farming}

### 2023-05-01 manuscript/manuscript.qmd
prepare manuscript for QI sub

```{r}
#| label: tbl-results
#| tbl-cap: Model Results
#| tbl-subcap:
#|   - "Parametric Terms"
#|   - "Smooth Terms"
#| layout-nrow: 2
#| layout: "[[1], [-1], [1]]"
#| out-width: 50%

# returns parametric and smooth regression tables
# and q, a list with character strings for reporting estimates in text
here::here("R", "regression-table.R") |> source()

parametric_table
smooth_table

>>>>

```{r}
#| label: tbl-results
#| tbl-cap: Model Results
#| output: asis

# tables in quarto are still a hot mess
cat(
"
\\begin{table}[]
\\centering
\\begin{tabular}{lllll}
\\textbf{Parametric Terms}  & \\textbf{exp ($\\beta$)}  & \\textbf{std.er} & \\textbf{t} & \\textbf{p-value} \\\\ \\midrule
Intercept                   & 0.00                      & 1.40             & -7.13       & \\textless{}0.001 \\\\ 
Maize GDD                   & 1.00                      & 0.001            & ~4.15       & \\textless{}0.001 \\\\ 
CD to Streams               & 0.67                      & 0.156            & -2.57       & ~~0.011           \\\\ 
Protected                   & 4.82                      & 0.497            & ~3.16       & ~~0.002           \\\\ \\bottomrule
                            &                           &                  &             &                   \\\\ 
                            &                           &                  &             &                   \\\\ 
\\textbf{Smooth Terms}      & \\textbf{edf}             & \\textbf{ref.df} & \\textbf{F} & \\textbf{p-value} \\\\ \\midrule
s(Precipitation)            & 3.25                      & 3.25             & 11.1        & \\textless{}0.001 \\\\ \\bottomrule
\\end{tabular}
\\end{table}
"
)

```{r}

here::here("R", "regression-table.R") |> source()

### 2023-05-01 manuscript/manuscript.tex
prepare manuscript for QI sub

\usepackage{booktabs}
\usepackage{caption}
\usepackage{longtable}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\journal{Quaternary International}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-num}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={The Fremont Frontier},
  pdfauthor={Kenneth B. Vernon; Peter M. Yaworsky; Weston McCool; Jerry D. Spangler; Simon Brewer; Brian F. Codding},
  pdfkeywords={Ideal Free Distribution, Great Basin, Paleoclimate
Reconstruction},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{keyword}
    Ideal Free Distribution \sep Great Basin \sep 
    Paleoclimate Reconstruction
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, interior hidden, breakable, sharp corners, enhanced, borderline west={3pt}{0pt}{shadecolor}, frame hidden]}{\end{tcolorbox}}\fi

@@

\begin{table}

\caption{\label{tbl-results}Model
Results}\begin{minipage}[t]{\linewidth}
\subcaption{\label{tbl-results-1}Parametric Terms }

{\centering

\setlength{\LTpost}{0mm}
\begin{longtable}{lcccc}
\tabularnewline

\toprule
 & \textbf{exp(Beta)} & \textbf{SE}\textsuperscript{\textit{1}} & \textbf{t} & \textbf{p-value} \\ 
\midrule
Intercept & 0.00 & 1.40 & -7.13 & <0.001 \\ 
Maize GDD & 1.00 & 0.001 & 4.15 & <0.001 \\ 
CD to Streams & 0.67 & 0.156 & -2.57 & 0.011 \\ 
Protected & 4.82 & 0.497 & 3.16 & 0.002 \\ 
\bottomrule
\end{longtable}
\begin{minipage}{\linewidth}
\textsuperscript{\textit{1}}SE = Standard Error\\
\end{minipage}

\end{minipage}%
\newline
\begin{minipage}[t]{\linewidth}
\subcaption{\label{tbl-results-2}Smooth Terms }

{\centering

\begin{longtable}{lcccc}
\tabularnewline

\toprule
 & \textbf{edf} & \textbf{ref.df} & \textbf{F} & \textbf{p-value} \\ 
\midrule
s(Precipitation) & 3.25 & 3.25 & 11.1 & <0.001 \\ 
\bottomrule
\end{longtable}

\end{minipage}%

\end{table}

>>>>

\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\journal{Quaternary International}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-num}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={The Fremont Frontier},
  pdfauthor={Kenneth B. Vernon; Peter M. Yaworsky; Weston McCool; Jerry D. Spangler; Simon Brewer; Brian F. Codding},
  pdfkeywords={Ideal Free Distribution, Great Basin, Paleoclimate
Reconstruction},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{keyword}
    Ideal Free Distribution \sep Great Basin \sep 
    Paleoclimate Reconstruction
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, enhanced, sharp corners, frame hidden, interior hidden]}{\end{tcolorbox}}\fi

@@

\hypertarget{tbl-results}{}
\begin{table}
\caption{\label{tbl-results}Model Results }\tabularnewline
[]
\centering
\begin{tabular}{lllll}
\textbf{Parametric Terms}  & \textbf{exp ($\beta$)}  & \textbf{std.er} & \textbf{t} & \textbf{p-value} \\ \midrule
Intercept                   & 0.00                      & 1.40             & -7.13       & \textless{}0.001 \\ 
Maize GDD                   & 1.00                      & 0.001            & ~4.15       & \textless{}0.001 \\ 
CD to Streams               & 0.67                      & 0.156            & -2.57       & ~~0.011           \\ 
Protected                   & 4.82                      & 0.497            & ~3.16       & ~~0.002           \\ \bottomrule
                            &                           &                  &             &                   \\ 
                            &                           &                  &             &                   \\ 
\textbf{Smooth Terms}      & \textbf{edf}             & \textbf{ref.df} & \textbf{F} & \textbf{p-value} \\ \midrule
s(Precipitation)            & 3.25                      & 3.25             & 11.1        & \textless{}0.001 \\ \bottomrule
\end{tabular}
\end{table}
